An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-09-29 paper.tex
Remove unnecessary todo
Tweak Figure captions

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/cite_counts_yearly.pdf}
  \caption{
    Citations from RFCs to other Internet-Drafts and RFCs per RFC
  }
  \label{fig:citations_year}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/keyword_usage_rate.pdf}
  \caption{
    Keyword occurrences per page
  }
  \label{fig:keyword_usage_rates}
\end{figure}

@@

\todo{Should we include ``Impact of Citations'' from TMA 2023?}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/cite_counts_yearly.pdf}
  \caption{
    Number of citations to other Internet-Drafts and RFCs per RFC in each
    year.
  }
  \label{fig:citations_year}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/keyword_usage_rate.pdf}
  \caption{
    Number of occurrences of normative language keywords per page in RFCs
    in each year.
  }
  \label{fig:keyword_usage_rates}
\end{figure}

@@

% \todo{Should we include ``Impact of Citations'' from TMA 2023?}
